Type Refinements for the Working Class

### 2015-11-12 paper.tex
Remove superfluous "Then"
Add some citations; reorder definitions

Then, for any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can
deploy a generic logical framework. Recall from \cite{sterling-morrison:2015}
that $\SCtx$ is the category of symbol-contexts and their injective,
sort-preserving renamings. Then, fix a small category $\mathcal{W}$ of worlds
along with a map $\Of{\pi_\mathcal{W}}{\mathcal{W}\to\SCtx}$ such that
$\pi_\mathcal{W}$ is a Grothendieck fibration. Then, a \emph{judgment} shall
be interpreted as an object in the presheaf category
$\Define{\mathbb{J}}{\Sets^{\OpCat{\mathcal{W}}}}$; in other words, a judgment
is identified with the intensional set of its renaming-sensitive derivations.

@@

\begin{definition}[Hypothetical Judgment]

  For two judgments $\mathcal{J}_1$ and $\mathcal{J}_2$, we can form the
  hypothetical judgment $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$, which expresses
  the semantic consequence of $\mathcal{J}_2$ from $\mathcal{J}_1$:
  \begin{align*}
    \ADefine{
      \left(\HypJ{\mathcal{J}_2}{\mathcal{J}_1}\right)(w)
    }{
      \left({\mathcal{J}_2}^{\mathcal{J}_1}\right)(w)
    }\\
    &\cong
    \OMode{
      \Hom{\mathbb{J}}{
        \Yoneda{w}\times\mathcal{J}_1
      }{
        \mathcal{J}_2
      }
    }\\
    &\cong
    \OMode{
      \int_{w'}{{{w'}\succeq{w}}\Rightarrow{{{\mathcal{J}}_{2}(w')}^{{\mathcal{J}}_{1}(w')}}}
    }
  \end{align*}

>>>>

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can
deploy a generic logical framework. Recall from \cite{sterling-morrison:2015}
that $\SCtx$ is the category of symbol-contexts and their injective,
sort-preserving renamings. Then, fix a small category $\mathcal{W}$ of worlds
along with a map $\Of{\pi_\mathcal{W}}{\mathcal{W}\to\SCtx}$ such that
$\pi_\mathcal{W}$ is a Grothendieck fibration~\cite{jacobs:2001}. Then, a
\emph{judgment} shall be interpreted as an object in the presheaf category
$\Define{\mathbb{J}}{\Sets^{\OpCat{\mathcal{W}}}}$; in other words, a judgment
is identified with the intensional set of its renaming-sensitive derivations.

\begin{definition}[Hypothetical Judgment]
  For two judgments $\mathcal{J}_1$ and $\mathcal{J}_2$, we can form the
  hypothetical judgment $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$ using the
  exponential construction~\cite[p.~46]{maclane-moerdijk:1992}, which expresses the semantic consequence
  of $\mathcal{J}_2$ from $\mathcal{J}_1$:
  \begin{align*}
    \ADefine{
      \left(\HypJ{\mathcal{J}_2}{\mathcal{J}_1}\right)(w)
    }{
      \left({\mathcal{J}_2}^{\mathcal{J}_1}\right)(w)
    }\\
    &\cong
    \OMode{
      \Hom{\mathbb{J}}{
        \Yoneda{w}\times\mathcal{J}_1
      }{
        \mathcal{J}_2
      }
    }\\
    &\cong
    \OMode{
      \int_{w'}{{{w'}\succeq{w}}\Rightarrow{{{\mathcal{J}}_{2}(w')}^{{\mathcal{J}}_{1}(w')}}}
    }
  \end{align*}

@@
